### 2022-10-23 Draft2.Rmd
progress

ggplot(data = tibble(all_abilities)) +
  geom_bar(aes(x = all_abilities))
```

@@

pokemon_copy %>% 
  unnest() %>% 
  View()
```

>>>>

#ggplot(data = tibble(all_abilities)) +
 # geom_bar(aes(x = all_abilities))
```

@@

pokemon_copy2 <- pokemon_copy %>% 
  unnest()

pokemon_copy2
```

```{r}
library(dplyr)

pokemon_abilities_grouped <- pokemon_copy2 %>% 
  group_by(abilities)

pokemon_abilities_grouped %>% 
  summarise(
    capture_rate = mean(capture_rate)
  ) %>% 
  arrange(desc(capture_rate))

```
